Split `r paste(params$species)` biomass by maturity class

### 2020-05-15 analysis/VOCC/1-split-biomass-by-maturity.Rmd
add option for sample_id_re to maturity splits with year effect

 try({ 
   maturity <- split_catch_maturity(survey_sets, fish, bath,
    survey = survey,
    years = years,
    year_re = TRUE,
    cutoff_quantile = c(.9995),
    p_threshold = threshold,
    plot = TRUE)
   })

  if(is.null(maturity$maturity)) {
  maturity <- split_catch_maturity(survey_sets, fish, bath,
    survey = c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG"),
    years = years,
    year_re = TRUE,
    cutoff_quantile = c(.9995),
    p_threshold = threshold,
    plot = TRUE
  )
  }

>>>>

 try({ 
   maturity <- split_catch_maturity(survey_sets, fish, bath,
    survey = survey,
    years = years,
    year_re = TRUE,
    # sample_id_re = TRUE,
    cutoff_quantile = c(.9995),
    p_threshold = threshold,
    plot = TRUE)
   })

  if(is.null(maturity$maturity)) {
  maturity <- split_catch_maturity(survey_sets, fish, bath,
    survey = c("SYN QCS","SYN HS","SYN WCVI","SYN WCHG"),
    years = years,
    year_re = TRUE,
    # sample_id_re = TRUE,
    cutoff_quantile = c(.9995),
    p_threshold = threshold,
    plot = TRUE
  )
  }
